### 2022-02-17 documentos/generators.tex
WHO THE FUCK CAME UP WITH MAKE?

A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map\cpnote{Creo que aun 
no tenemos el link entre el generador y la matriz A}.
Consider the map $\Sigma^{(k)}$ that reflects an index $\valpha$ with 
respect to the $k$-th axis. This map leaves all components of $\valpha$
invariant, except the $k$-th component, which is transformed according to 
\begin{equation}
% \Sigma: 
0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1. 
\label{eq:Sigma}
\end{equation}
% and the associated 
All $N$ maps have the following properties:
\begin{enumerate}
\item $\Sigma^{(k)}(\vec\alpha)\oplus \Sigma^{(k)}(\vec\beta)=\vec\alpha\oplus \vec\beta$.
\item $\Sigma^{(k)}(\vec\alpha)\neq\vec\alpha$.
\end{enumerate}
From the first property, we now obtain
\begin{equation}
\valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0), 
\label{eq:Sigma}
\end{equation}
which means that if $\Sigma^{(k)}(\vec0)$ belongs
to a channel then 
$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}$, where we used 
the fact that for channels, the non-zero elements are closed
under $\oplus$. In other words, the components of a PCE channel
are symmetric under reflection over the $k$-th axis. \cpnote{Quizá 
referencia a algunas figuras}. Now consider the case in which 
 $\Sigma^{(k)}(\vec0)$ does not belong to generator. Then 
$\tau_\valpha \ne \tau_{\Sigma^{(k)}(\vec\alpha)}$, since
the case $\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=1$
is forbidden due to \eref{eq:Sigma} and the case 
$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=0$ is also forbidden 
because for generators, the codimension of the associated vector space 
is 1.

% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

\janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
For instance, see that the 2-qubit PCE generators 
$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
respectively, are either symmetric or anti-symmetric under reflection with 
respect to lines that divide the diagram in half vertically and horizontally. 
The same symmetry is identified for the rows and columns of $A$ if one 
labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
\janote{Aquí habría que agregar la prueva de simetría para la $A$.}

@@

\cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
del primer parrafo}

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

The set of all PCE quantum channels may be sorted in subsets, 
which we will call equivalence classes, whose
elements are equivalent via particle swaps and local-basis element
permutations. 
\janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
Aún hay que decidirlo con los demás.}

>>>>

A reflection symmetry is identified for both PCE generators $\pceg$ and
matrix $A$ \cpnote{Creo que aun 
no tenemos el link entre el generador y la matriz A}.
Consider the map $\Sigma^{(k)}$ that reflects an index $\valpha$ with 
respect to the $k$-th axis. This map leaves all components of $\valpha$
invariant, except the $k$-th component, which is transformed according to 
\begin{equation}
% \Sigma: 
0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1. 
\label{eq:Sigma}
\end{equation}
% and the associated 
The maps have the following properties:
\begin{enumerate}
\item $\Sigma^{(k)}(\vec\alpha)\oplus \Sigma^{(k)}(\vec\beta)=\vec\alpha\oplus \vec\beta$, and
\item $\Sigma^{(k)}(\vec\alpha)\neq\vec\alpha$.
\end{enumerate}
From the first property, we now obtain
\begin{equation}
\valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0). 
\label{eq:Sigma}
\end{equation}
This implies that if $\Sigma^{(k)}(\vec0)$ belongs
to a channel then 
$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}$, where we used 
the fact that for channels, the non-zero elements are closed
under $\oplus$. In other words, the components of a PCE channel
are symmetric under reflection over the $k$-th axis. Now consider the case in which 
 $\Sigma^{(k)}(\vec0)$ does not belong to generator. Then 
$\tau_\valpha \ne \tau_{\Sigma^{(k)}(\vec\alpha)}$, since
the case $\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=1$
is forbidden due to \eref{eq:Sigma} and the case 
$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=0$ is also forbidden 
because for generators, the codimension of the associated vector space 
is 1. This means that the components of a PCE channel are antisymmetric
with respect to reflection over the $k$-th axis. 
Indeed, the 2-qubit PCE generators 
$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
respectively, are either symmetric or anti-symmetric under reflection with 
respect to lines that divide the diagram in half vertically and horizontally.

\cpnote{De aca al resto de la seccion o establecemos la conexion con A o lo quitamos}
% 
% 
% The symmetry for a PCE generator $\pceg$ is encoded in the 
% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
% is either symmetric or anti-symmetric under reflection of the 
% indices in the $k$-th position in $\vec\alpha$. 
% Consider the map
% \begin{equation}
% % \Sigma: 
% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
% \label{eq:Sigma}
% \end{equation}
% Indeed, any generator is a subspace containing half the elements of the full vector space.  
% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
% \begin{enumerate}
% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
% \end{enumerate}
% From the first property, we now obtain
% \begin{equation}
% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
% \end{equation}
% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
%

% \janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
% For instance, see that the 2-qubit PCE generators 
% $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
% represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
% respectively, are either symmetric or anti-symmetric under reflection with 
% respect to lines that divide the diagram in half vertically and horizontally. 
The same symmetry is identified for the rows and columns of $A$ if one 
labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
\janote{Aquí habría que agregar la prueva de simetría para la $A$.}

@@

% \cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
% del primer parrafo}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
% 
% The set of all PCE quantum channels may be sorted in subsets, 
% which we will call equivalence classes, whose
% elements are equivalent via particle swaps and local-basis element
% permutations. 
% \janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
% Aún hay que decidirlo con los demás.}
